The goal of implementing a working \gls{trng} was not reached during this lab assignment. 

The number generation was extremely deterministic, as the p-values obtained by the NIST Test
Suite score all a 0. The Test Suite (and also its wrapper) throw many igamc: UNDERFLOW
errors that were at first wrongfully interpreted as errors due to the used compiler and
the used math libraries. 
After further investigation this just means that the p-value is so low that an exception
is thrown and the p-value gets replaced by 0. 

As a good p value should be around 0.5 (equal chance of guessing and not guessing the
correct sequence) the conclusion must be drawn that the numbers are not suitable for
cryptography at all. 

Interestingly enough a run with the dieharder test suite yields good results on the same
data. Further investigation is needed on the why.

\begin{table}[htp]
	\centering
	\caption{Dieharder results for experiment TRNG}
	\label{tbl:results}
	\begin{tabular}{lccc}

		\hline
		\textbf{Test} & \textbf{tSample} &\textbf{P-value} &\textbf{Passed} \\
		\hline
         sts_monobit&       100000&     0.18544306&  PASSED  \\ 
            sts_runs&       100000&     0.95997337&  PASSED  \\
          sts_serial&       100000&     0.13818581&  PASSED  \\
          sts_serial&       100000&     0.99575888&   WEAK   \\
		\hline
	\end{tabular}

\end{table}
\begin{table}[htp]
	\centering
	\caption{NIST-STS results for experiment XYZ}
	\label{tbl:NISTresults}
	\begin{tabular}{lc}

		\hline
		\textbf{Test} & \textbf{P-value} \\
		\hline

		Frequency & 0.0\\
		Block Frequency & 0.0\\
		... & 0.0\\
		Complexity & 0.0\\
		\hline

	\end{tabular}

\end{table}

\subsubsection{Design and Testing}
A random number takes 128 cycles to be generated, at 100MHz one 128bit random number
therefore needs 1.28us. Considering the UART Overhead and the wait time of 0.01ms in the
python script that reads from UART the generation of 100000 random numbers takes around 10
minutes. Testing with the dieharder testsuite takes around 10 minutes, the NIST Test
Suites are finished after 1 minute.

\begin{table}[htp]
	\centering
	\caption{Utilization of the project}
	\label{tbl:utilResults}
	\begin{tabular}{lcccc}

		\hline
        Site Type& Used & Fixed & Available & Util\% \\
		\hline
 Slice LUTs              &  517 &   128 &     63400 &  0.82 \\
   LUT as Logic          &  517 &   128 &     63400 &  0.82 \\
   LUT as Memory         &    0 &     0 &     19000 &  0.00 \\
 Slice Registers         &  442 &     1 &    126800 &  0.35 \\
   Register as Flip Flop &  442 &     1 &    126800 &  0.35 \\
   Register as Latch     &    0 &     0 &    126800 &  0.00 \\
 F7 Muxes                &    5 &     0 &     31700 &  0.02 \\
 F8 Muxes                &    0 &     0 &     15850 &  0.00 \\
		\hline

	\end{tabular}

\end{table}
